R Notebook

### 2021-10-04 documentation_and_analysis/draftbook.Rmd
Edits

```{r}
uk_ev_income %>% 
  ggplot() +
  aes(x = x2021_q1_log, y = mean_total_annual_income) +
  geom_point() +
  geom_smooth(method = lm, colour = "#08a44c", se = FALSE) +
  theme_minimal() +
  labs(title = "\nEVs vs Mean Annual Income for Local Authorities in England and Wales\n",
       x = "\nTotal Number of EV Chargers (log)\n",
       y = "\nMean Total Annual Income\n") +
  png("ev_income.png", units="in", width=8, height=5, res=300)
```

>>>>

```{r}
uk_ev_income %>% 
  ggplot() +
  aes(x = x2021_q1_log, y = mean_total_annual_income) +
  geom_point() +
  geom_smooth(method = lm, colour = "#08a44c", se = FALSE) +
  theme_minimal() +
  labs(title = "\nEVs vs Mean Annual Income for Local Authorities in England and Wales\n",
       x = "\nNumber of Electric Vehicles (log)\n",
       y = "\nMean Total Annual Income\n") +
  png("ev_income.png", units="in", width=8, height=5, res=300)
```
